Making all equalities equal

### 2021-09-23 paper.lagda.tex
redefined from previous theorem

% \end{code}
% \begin{code}

@@

          in _≡_ {ℓ-suc ℓ₁} x≣y x≡y
\end{code}

@@

\begin{code}
      ≡-≡-≣ : {x y : A} → let
        x≡y : Type ℓ₁
        x≡y = x ≡₁ y
        x≣y = x ≣ y
        in x≡y ≡ x≣y
      ≡-≡-≣ = sym ≣-≡-≡

      instance
        ≣-isEquality : IsEquality _≣_
        ≣-isEquality = eq (≣-≡-≡ ∙ IsEquality.≣-≡-≡ eq₁)

      instance
        ≡₂-Equality₂ : IsEquality₂ _≡₂_
        ≡₂-Equality₂ = eq (eq₂ .≣-≡-≡ ∙ sym (eq₁ .≣-≡-≡))
          where open IsEquality

      alwaysEqual : ∀ {x y} →  x ≡₁ y → x ≡₂ y
      alwaysEqual {x} {y} p =
        let joined = sym (≣-≡-≡ {x} {y})
        in transport joined p
        where open IsEquality₂ ≡₂-Equality₂

@@

>>>>

@@

      ≡-≡-≣ : {x y : A} → let
        x≡y : Type ℓ₁
        x≡y = x ≡₁ y
        x≣y = x ≣ y
        in x≡y ≡ x≣y
      ≡-≡-≣ = sym ≣-≡-≡

@@

\begin{code}
      instance
        ≣-isEquality : IsEquality _≣_
        ≣-isEquality = eq (≣-≡-≡ ∙ IsEquality.≣-≡-≡ eq₁)
\end{code}

From a more generic defintion of equality,
it is easily possible to return to the less generic definition.

\begin{code}
    module _
      (Eq₂ : Equality {_} {ℓ} {A})
      where

      open Equality Eq₂ renaming (_≣_ to _≡₂_; isEquality to eq₂)
\end{code}

I am defining a new generic equality to prove that it is
an equality of type 2:

% \end{code}
%
% \begin{code}

      eqsEqual₂ : ∀ {x y} → let
        x≣₁y : Type ℓ₁
        x≣₁y = x ≡₁ y

        x≣₂y : Type ℓ₁
        x≣₂y = x ≡₂ y

        in _≡_ {ℓ-suc ℓ₁} x≣₁y x≣₂y
      eqsEqual₂ = eqsEqual _≡₁_ _≡₂_

      instance
        ≡₂-Equality₂ : IsEquality₂ _≡₂_
        ≡₂-Equality₂ = eq (sym eqsEqual₂)
          where open IsEquality

@@

Given a symmetric definition of the previous equality,
it is easy to prove that it is also an equality of type 2.
